Tabular Constraint Learning

### 2016-04-01 Paper/ECAI/tabular.tex
refactoring the tex file

\usepackage[dvipsnames]{xcolor}
\newcommand{\sergey}[1]{\textcolor{magenta}{{\sc Sergey} #1}\xspace}

@@

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
\sergey{bullet points for luc to start introduction}\\
\textbf{Key question}:\\
Can we discover or reconstruct structural relations in flat tabular spreadsheet data? [in a general way that allows declarative specification of constraints to discover]\

\textbf{Motivation}:
\begin{itemize}
  \item File generated from model, model got lost - > reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

\sergey{we need structure here}

>>>>

\usepackage[dvipsnames]{xcolor}
\newcommand{\sergey}[1]{\textcolor{magenta}{{\sc Sergey:} #1}\xspace}

@@

\begin{abstract}
  abstract
  \end{abstract}
\section{Introduction}
\sergey{bullet points for luc to start introduction}\\
\textbf{Key question}:\\
Can we discover or reconstruct structural relations in flat tabular spreadsheet data? [in a general way that allows declarative specification of constraints to discover]\\

\textbf{Motivation}:
\begin{itemize}
  \item File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

\sergey{to himself we need structure here}
